Paper notes

### 2019-08-07 paper_notes.Rmd
single run function

# Calculation ethnic utility (for each option)

@@

>>>>

# Calculation ethnic utility (for each option)
# i_e: ethnic threshold (ideal point)
# M: right-side slope
# x: number agents in neighborhood with same color
# n: total number agents in neighborhood
# S: left-side slope
# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)

@@

Specify n > x <- U:NA in formula

```{r ethnic utility individual-run include=TRUE, echo=FALSE}

i_e = 0.5
M = 0
S = 1
n = 8
